Untitled

### 2020-09-07 KB_model_2.Rmd
Updated plots more and added to paper
added more to paper
Added more to Paper

```{r libs}
library(tidyverse)
library(tidymodels)
```

@@

# 
# dat_split <- initial_split(dat)
# 
# train_dat <- training(dat_split)
# test_dat <- testing(dat_split)
```

@@

dat_annual <- dat_annual %>%
  add_predictions(
    fit_overall,
    var = "pred_overall"
  ) %>%
  mutate(
    resid_annual = ghits_annual - pred_overall
  )
```

@@

@@

@@

```{r}
lm(resid_final ~ team:phase, data = dat)
```

>>>>

```{r libs}
library(tidyverse)
library(tidymodels)
library(lubridate)
library(modelr)
```

@@

dat %>%
  write.csv("Model_Data.csv")
# 
# dat_split <- initial_split(dat)
# 
# train_dat <- training(dat_split)
# test_dat <- testing(dat_split)
```

@@

summary(fit_overall)

dat_annual <- dat_annual %>%
  add_predictions(
    fit_overall,
    var = "pred_overall"
  ) %>%
  mutate(
    resid_annual = ghits_annual - pred_overall
  )

```

@@

summary(fit_annual)

@@

summary(fit_monthly)

@@

```{r}
test <- lm(resid_final ~ team:phase, data = dat)
```
